Detailed structure of phospholipid bilayers with negatively charged lipids and salt concentrations from molecular dynamics simulations including the effects of electronic polarization

### 2019-05-13 Manuscript/manuscript.tex
Improved Title of the paper

%%SAMULI: new suggestion for the preliminary title
\title[] 
  { Non-negligible Effects of Electronic Polarization at Negatively Charged Membranes with Ions }

>>>>

%%SAMULI: new suggestion for the preliminary title
\title[] 
  { Detailed structure of phospholipid bilayers with negatively charged lipids and salt concentrations 
    from molecular dynamics simulations including the effects of electronic polarization }
 %{ Non-negligible Effects of Electronic Polarization at Negatively Charged Membranes with Ions }
 %{ Effective Inclusion of Electronic Polarization to a Negatively Charged Membrane }
